Composition-climate paper

### 2016-08-22 Composition_Ecology.Rmd
Started workon the methods but got distracted.
Adding a `tif` and a figure output.

*This section should contain sufficient detail so that all procedures can be repeated (in conjunction with cited references). A checklist is provided so that authors can check that their methods report details which our editors regard as essential. This checklist is available here. Where specific equipment and materials are named, the manufacturer's name, city and country should be given (generally in parentheses after first mention).*

@@

Settlement-era forest data are based on survey data from the Public Land Survey System [PLS: @white1983history;@schulte2001original;@gorng2016preset], aggregated to a 64 km^2 grid across the upper Midwestern United States [@gorng2016preset]. We briefly review the methods here. PLS data originally were collected on a 1 x 1 mi grid across the Upper Midwest from 1830 - 1904 [@schulte2001original;@almendinger1996minnesota;@white1983history]. At each survey, point surveyors noted the closest two to four trees and recorded their common name, distances to the survey point, diameters at breast height and azimuth to the tree. Goring et al. [-@gorng2016preset] aggregated this data to an 8x8 km grid, resulting in a gridded data product with an average of 61 survey points per cell, or approximately 120 trees per cell. This process included data cleaning, taxonomic standardization, and the application of spatially varying correction factors [@gorng2016preset]. Using the count data produced by Goring et al. [-@gorng2016preset], we produce presence-absence distributions for each taxon, across the upper Midwest for 15 common tree genera (`r tab_nums("genera_table", display = "cite")`). Common names for certain taxa, such as "Ironwood" can not be clearly resolved to a single tree genera, as such we combine *Ostrya* and *Carpinus* (ironwood), and *Thuja* and *Juniperus* (cedar). Here presence is defined as at least one recorded tree in any 8x8 km grid cell.

>>>>

@@

Estimates of settlement-era forest composition and tree distribution based on survey data from the Public Land Survey System [PLS: @white1983history;@schulte2001original;@gorng2016preset], aggregated to a 64 km^2 grid across the upper Midwestern United States [@gorng2016preset]. We briefly review the methods here. PLS data originally were collected on a 1 x 1 mi grid across the Upper Midwest from 1830 - 1904 [@schulte2001original;@almendinger1996minnesota;@white1983history]. At each survey, point surveyors noted the closest two to four trees and recorded their common name, distances to the survey point, diameters at breast height and azimuth to the tree. Goring et al. [-@gorng2016preset] aggregated this data to an 8x8 km grid, resulting in a gridded data product with an average of 61 survey points per cell, or approximately 120 trees per cell. This process included data cleaning, taxonomic standardization, and the application of spatially varying correction factors [@gorng2016preset]. Using the count data produced by Goring et al. [-@gorng2016preset], we produce presence-absence distributions for each taxon, across the upper Midwest for 15 common tree genera (`r tab_nums("genera_table", display = "cite")`). Common names for certain taxa, such as "Ironwood" can not be clearly resolved to a single tree genera, as such we combine *Ostrya* and *Carpinus* (ironwood), and *Thuja* and *Juniperus* (cedar). Here presence is defined as at least one recorded tree in any 8x8 km grid cell.
